NFC and burnout in teachers - A replication and extension study

### 2021-10-29 Manuscript/Manuscript.Rmd
finished results of exploratory1

The first exploratory analysis concerned a modification of the demand-resource-model in which the subscale reduced personal efficacy would be used in place of the MBI sum score.
The total, direct, and indirect effects are listed in **Supplementary Table**.
Similar to the previous model, this model's indices did not indicate good fit with a Chi-square statistic of $\chi^2 = $`r round(fit_explor1@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), a CFI of `r round(fit_explor1_summ[["FIT"]][["cfi.robust"]], digits = 2)`, a SRMR of `r round(fit_explor1_summ[["FIT"]][["srmr"]], digits = 2)`, and a RMSEA of `r round(fit_explor1_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
NFC showed no direct association with reduced personal efficacy ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "c"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "c"], digits = 3)`), but an indirect one via higher scores in the latent variable DRF ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect3"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect3"], digits = 3)`).
And again, NFC was associated with lower scores in the latent variable DTH ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a1"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a1"], digits = 3)`), but the latter did not mediate the relationship between NFC and reduced personal efficacy ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect1"], digits = 3)`) as it did with the MBI score in the previous model.
Instead, NFC showed indirect negative associations with the MBI score via lower scores in the latent variable DTH ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect1"], digits = 3)`) and via higher scores in the latent variable DRF ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect3"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect3"], digits = 3)`).
The latent variable DTL was neither related to NFC ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a2"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "b2"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "b2"], digits = 3)`).

>>>>

The first exploratory analysis concerned a modification of the demand-resource-model in which the subscale reduced personal efficacy would be used in place of the MBI sum score.
The total, direct, and indirect effects are listed in **Supplementary Table**.
Similar to the previous model, this model's indices did not indicate good fit, with a Chi-square statistic of $\chi^2 = $`r round(fit_explor1@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$), a CFI of `r round(fit_explor1_summ[["FIT"]][["cfi.robust"]], digits = 2)`, a SRMR of `r round(fit_explor1_summ[["FIT"]][["srmr"]], digits = 2)`, and a RMSEA of `r round(fit_explor1_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit_explor1_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
NFC showed no direct association with reduced personal efficacy ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "c"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "c"], digits = 3)`), but an indirect one via higher scores in the latent variable DRF ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect3"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect3"], digits = 3)`).
And again, NFC was associated with lower scores in the latent variable DTH ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a1"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a1"], digits = 3)`), but the latter did not mediate the relationship between NFC and reduced personal efficacy ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "Indirect1"], digits = 3)`) as it did with the MBI score in the previous model.
The latent variable DTL was neither related to NFC ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "a2"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta = $`r round(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label == "b2"], digits = 2)`, $p = $`r round(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label == "b2"], digits = 3)`).
